%Input preamble
\input{preamble}
\input{output/mainstatistics}

\newcommand*\leftright[2]{%
  \leavevmode
  \rlap{#1}%
  \hspace{0.5\linewidth}%
  #2}

\newcommand{\orth}{\ensuremath{\perp\!\!\!\perp}}%
\newcommand{\indep}{\orth}%
\newcommand{\notorth}{\ensuremath{\perp\!\!\!\!\!\!\diagup\!\!\!\!\!\!\perp}}%
\newcommand{\notindep}{\notorth}

\externaldocument{abc_treatmenteffects_appendix}
\pagenumbering{roman}

\begin{document}

\begin{titlepage}
\newgeometry{top=.8in, bottom=.8in, left=.8in, right=.8in}

\title{\Large \textbf{Gender Differences in\\ the Benefits of an Influential Early Childhood Program}\thanks{This research was supported in part by grants from the Robert Wood Johnson Foundation's Policies for Action program, NICHD R37HD065072, the American Bar Foundation, the Buffett Early Childhood Fund, the Pritzker Children's Initiative, NICHD R01HD054702, NIA R01AG042390, and by the National Institute On Aging of the National Institutes of Health under Award Number P30AG024968. The views expressed in this paper are solely those of the authors and do not necessarily represent those of the funders or the official views of the National Institutes of Health. The authors wish to thank Frances Campbell, Craig and Sharon Ramey, Margaret Burchinal, Carrie Bynum, Elizabeth Gunn, and the staff of the Frank Porter Graham Child Development Institute at the University of North Carolina Chapel Hill for the use of data and source materials from the Carolina Abecedarian Project and the Carolina Approach to Responsive Education. They also assisted with information on the implementation of the studied interventions. Years of partnership and collaboration have made this work possible. We thank Ruby Zhang for excellent research assistance. Collaboration with Andr\'{e}s Hojman, Yu Kyung Koh, Sylvi Kuperman, Stefano Mosso, Rodrigo Pinto, Joshua Shea, and Jake Torcasso on related work has strengthened the analysis in this paper. For helpful comments on various versions of the paper, we thank the editor, three anonymous referees, St\'{e}phane Bonhomme, Fl\'{a}vio Cunha, Steven Durlauf, David Figlio, Marco Francesconi, Dana Goldman, Ganesh Karapakula, Sidharth Moktan, Rich Neimand, Tanya Rajan, Azeem Shaikh, Jeffrey Smith, Chris Taber, Matthew Tauzer, Ed Vytlacil, Jim Walker, and Matt Wiswall. We benefited from helpful comments received at the Leonard D. Schaeffer Center for Health Policy and Economics in December, 2016, and at the University of Wisconsin, February, 2017. For information on childcare in North Carolina, we thank Richard Clifford and Sue Russell. The set of codes to replicate the computations in this paper are posted in a repository. Interested parties can request to download all the files. The address of the repository is \url{https://github.com/jorgelgarcia/abccare-cba}. To replicate the results in this paper, contact any of the authors, who will put you in contact with the appropriate individuals to obtain access to restricted data. The Appendix for this paper is posted on \url{http://cehd.uchicago.edu/ABC_CARE}.}}

\author{
Jorge Luis Garc\'{i}a\\
Department of Economics\\
The University of Chicago \and
James J. Heckman \\
American Bar Foundation \\
Department of Economics\\
The University of Chicago \and
Anna L. Ziff \\
Center for the Economics of \\
Human Development \\
The University of Chicago}
\date{First Draft: January 5, 2016\\ This Draft: \today \\}

\maketitle
\thispagestyle{empty}
\restoregeometry
\end{titlepage}

\thispagestyle{empty}
\singlespacing
\begin{abstract}
\input{sections/0_abstract}
\end{abstract}

\noindent \textbf{Keywords}: Gender differences, childcare, early childhood education, randomized trials, substitution bias \\
\noindent \textbf{JEL codes}: J13, I28, C93\\


\bigskip
\begin{tabular}{ll}
Jorge Luis Garc\'{i}a                                       & James J. Heckman \\
Department of Economics                                & Department of Economics \\
University of Chicago                                       & University of Chicago \\
1126 East 59th Street                                     & 1126 East 59th Street \\
Chicago, IL 60637                                           & Chicago, IL 60637 \\
Phone: 773-449-0744                                    & Phone: 773-702-0634  \\
Email: jorgelgarcia@uchicago.edu                       & Email: jjh@uchicago.edu \\
                                                                       & \\
Anna L. Ziff                                         &  \\
Center for the Economics of & \\
Human Development            & \\
University of Chicago                                        &  \\
1126 East 59th Street                       & \\
Chicago, IL 60637                                              &       \\
Phone: 734-277-7379                                    &  \\
Email: aziff@uchicago.edu                     &  \\

\end{tabular}

\clearpage

\vspace{3 em}
\noindent \textbf{[JJH: I need the web appendix---not printed.][This is printed now.]} \\

\noindent \textbf{[JJH: Before we spoke about low quality childcare harming boys. Now suddenly this has gone and replacing it wis high quality home environments for boys. Are we so sure?]} \\

\noindent \textbf{This does not contradict what we have before. Before we stated the finding as ``boys being harmed by low quality program.'' But there is much more to this. In general, girls are more disadvantaged than boys so it needs to be the case that they face a worst treatment counterfactual, whether they stay at home or go to an alternative preschool (Panel (b) of Figure 2).} \\

\noindent \textbf{When exploring within-girls and within-boys is when we are able to better understand the interpretation of the different parameters that we estimated. Boys who are more disadvantaged more often go to alternatives (Panel (d), Figure 2). For girls, the reverse is true (Panel (c) of Figure 2). Then, boys benefit more from treatment if compared than alternatives than if compared to staying at home (at home their environment is better, else they are more disadvantaged and also they face a low quality alternative) --- as we discussed in the previous version. Girls benefit more from alternatives because else they would face a relatively worst home environment --- which we also discussed in the previous version.} \\

\noindent \textbf{We perform tests to verify that the patterns in Figure 2 are statistically significant and all of the batteries of tests agree to this interpretation: average effects sizes (which are nuts but a referee seems to obsess about them), combining functions (of the two types that we discusses), and the new tests (Rosenbaum).}
\vspace{3 em}

\clearpage

\restoregeometry
\doublespacing


\setcounter{page}{0}
\pagenumbering{arabic}

\setlength\parindent{0pt}
\setlength{\parskip}{10pt}

\section{Introduction}
\label{sec:introduction}
\input{sections/1_introduction}	

\section{Data}
\label{sec:data}
\input{sections/2_data}

\section{Parameters of Interest}
\label{sec:parameters}
\input{sections/3_parameters}

\section{Estimates and Tests}
\label{sec:treatment-effects}
\input{sections/4_treatment-effects}

\section{Explaining Gender Differences}
\label{sec:gender-differences}
\input{sections/5_gender-differences}

\section{Conclusion}
\label{sec:conclusion}
\input{sections/6_conclusion}

\singlespacing
\bibliography{heckman}
\bibliographystyle{chicago}

\end{document}
