\section{Background Variables and Tested Outcomes} \label{appendix:controls}
\subsection{Controlling for Background Variables}

\noindent We select the background variables that we control for as follows. First, we select the three variables, from 17 potential variables, that best predict enrollment into alternative preschool for subjects who were randomly assigned not to receive center-based childcare---the control group in ABC and the control and family education treatment groups in CARE. To choose the most predictive control set, we estimate the $17 \choose 3$ linear models, using the variables in Panels (1) and (2) of Table~\ref{tab:pselectvars}. The most predictive model is the one generating the lowest Bayesian Information Criterion (BIC).\\

\noindent We proceed in a similar way to choose the second set of background variables. Instead of predicting enrollment into alternative preschool, we predict the relevant outcome of interest. For this exercise we use the variables in Panel (2), so we estimate $14 \choose 3$ models.\\

\noindent Our set of control variables consists of these two sets of background variables.

\singlespacing
\input{output/controlsets}
\doublespacing
\subsection{Tested Outcomes}

\noindent The following table lists the 95 main outcomes that are used in the cost/benefit analysis. Appendix~\ref{appendix:moreoutcomes} presents treatment effects for a larger set of outcomes. We reverse the outcomes for which we consider a negative treatment effect socially positive.

\singlespacing
\input{output/abccare_outcomes_list}
\doublespacing
